Model Building

### 2020-07-30 Model_Build.Rmd
Added comments around model building

# ARIMA is used when implementing exogenous regressors

@@

fitted %>%
  ggplot() + 
  geom_line(aes(x = date, y = googlehits), color = "blue") +
  geom_line(aes(x = date, y = .fitted), color = "red")

@@

coef
```

>>>>

# ARIMA is used when implementing exogenous regressors so Arima works for our data
# from what I have seen, the date doesn't need to me on the right hand side of the formula
# I believe you can manually add seasonality if you specify your own model; however, it should estimate seasonality if I don't specify it

@@

#PLOT of Actual vs Fitted Values
fitted %>%
  ggplot() + 
  geom_line(aes(x = date, y = googlehits), color = "blue") +
  geom_line(aes(x = date, y = .fitted), color = "red")

@@

coef
# exogenous regressors are still not significant though?
```
